\documentclass{article}
\usepackage{amsmath,amsthm,parskip}
\usepackage[utf8]{inputenc}
%\pagenumbering{gobble}
\begin{document}

Name:\\
\medskip
Section (time):

\subsection*{Math 340 Quiz 1}


1.) $G=\left[\begin{array}{cccc}
0 & 1 & 1 & 0\\
1 & 0 & 0 & 1\\
1 & 0 & 0 & 1\\
0 & 1 & 1 & 0
\end{array}\right]$. 

2.) Write the following system of equations in the form $Ax = b$

$$10x_1+9x_2+x_3-9=0$$
$$9x_2+x_3+1=0$$
$$10x_1 - x_3=8$$


\pagebreak
Math 340 9/14

i.) Consider $A=\left[\begin{array}{cccccccc}
1 & 1 & 1 & 0 & 0 & 1 & 1 & 0\\
1 & 0 & 0 & 1& 0 & 1 & 1 & 0\\
1 & 8 & 0 & 1 & 777 & 1 & 1 & 0\\
1 & 0 & 0 & 9 & 0 & 1 & 1 & 0\\
1 & 5 & 0 & 1 & 0 & 1 & 1 & 0\\
1 & 0 & 0 & 1 & 0 & 27 & 1 & 0\\
1 & 0 & 44 & 1 & 0 & 1 & 3 & 0\\
0 & 1 & 1 & 0 &0 & 1 & 1 & 0
\end{array}\right]$.

Let B = 2A and $C=AB$ and $D=C^T$.

Find $d_{81}$.


\bigskip

ii.) $A=\left[\begin{array}{cc}
0 & 1 \\
0 & 1
\end{array}\right]$

and $B=\left[\begin{array}{cc}
0 & 1 \\
0 & 0
\end{array}\right]$

Find $AB$. Find $C=BA$. Find $C^2$.


iii.) Suppose $AB=0$ and $C=BA$. What can you say about $C^2$? Support your claim. 



iv.) The following is an example of a \emph{shift matrix}, 
$$S = \left[\begin{array}{ccc}
0 & 1 & 0\\
0 & 0 & 1\\
0 & 0 & 0
\end{array}\right].$$

Why is it called that? Try computing $SA$ and $AS$ for

$$A = \left[\begin{array}{ccc}
a & b & c\\
d & e & f\\
g & h & i
\end{array}\right].$$

Try also $$B = \left[\begin{array}{ccc}
r & s \\
t & u  \\
v & w 
\end{array}\right].$$

\pagebreak

Math 340 9/14 Solutions

i.) $d_{81}=0$. That is, entry $(8,1)$ of $D$ is zero.

We know that matrix $D$ is the transposition of matrix $C$.

Therefore, we are trying to compute $c_{18}=d_{81}$. 

We are given $C=AB=A2A=2A^2$. 

Therefore, $c_{18}=2a^2_{18}$. 

Recall the entry $(i,j)$ from a matrix that is the product of two matrices will be equal to the $i^{\text{th}}$ \emph{row} of the first matrix dot producted with the $j^{\text{th}}$ \emph{column} of the second matrix. So, we take the first row of $A$ and dot that with the last column. Note the last column is all zeros. Therefore the dot product will be zero, and $a^2_{18}=0$.

Now, $d_{81}=c_{18}=2a^2_{18}=2\times 0 =0$.


\bigskip

ii.) $C^2$ is a $2\times2$ matrix of all zeros. 

\bigskip

iii.) This is an exercise in squaring matrices and using associativity of matrix multiplication. 


We are given $C=BA$ and asked to compute $C^2$. 

$C^2=BABA$, \emph{note that} $C^2\neq B^2A^2$.

Using associativity, $C^2 = B(AB)A = B0A=0$. 

iv.) 

$$SA= \left[\begin{array}{ccc}
d & e & f\\
g & h & i\\
0 & 0 & 0 \\
\end{array}\right]$$

$$AS= \left[\begin{array}{ccc}
0& a & b \\
0& d & e \\
0& g & h 
\end{array}\right]$$

$$SB =\left[\begin{array}{ccc}
t & u\\
v & w \\
0 & 0
\end{array}\right]$$

Please note $BS$ is not computable. $B$ is of dimension $3\times 2$ and $S$ is of dimension $3\times 3$. The first matrix in a product must have the same number of columns and the second matrix has rows. This ensures that the dot products featured in matrix multiplication will be defined. 


\end{document}
